Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-14 doc/GMP2015/s02_preliminaries.tex

In the context of this paper, a \textbf{graph} $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$.

The \textbf{density} of graph $G$ is
\begin{equation}
    d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}
\end{equation}

A graph is \textbf{independent} (or \textbf{sparse}) if \todo{define}.

A graph is \textbf{over-constrained} if, given constant $k$, there exists some induced subgraph $S\subseteq G$ such that $d(S) > k$.

A graph is \textbf{well-constrained} if, given constant $k$, $d(G) = k$ and for all induced subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).

A graph is \textbf{rigid} if, given constant $k$, there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.

A graph is \textbf{under-constrained} if, given constant $k$, $G$ is not rigid.

A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an over-constrained graph and (2) all of its subgraphs are also trivial.
\todo{Maybe leave the following out until it's needed later?}
In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.

The \textbf{decomposition-recombination (DR-) plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
\begin{enumerate}
    \item The root of the tree `contains' $G$.
    \item For all nodes, $C$, that `contain' nontrivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
    \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
    \item A node with a trivial subgraph is a leaf.
\end{enumerate}
% It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its well-constrained vertex-maximal proper subgraphs whose union is $G$ itself.

@@

Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.

The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \textit{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.

The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.

@@

$G$ is taken to be a graph with values $(V,E,w_V,w_E)$. To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them. Furthermore, to limit the scope of the paper, $G$ will always be taken to be well-constrained.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

>>>>

% TODO

% A paragraph of preliminaries such as rigidity matrix R, stress vectors S one coordinate per edge (w/ SR =E (external stress vector, 2 coordinates  per vertex)); flex vectors F (2 coordinates per vertex) (right nullspace/kernel of R) should precede the definition of independent, overconstrained (not independent), rigid (contains an independent set with sufficiently many eedges/constraints) isostatic (wellconstrained/minimally rigid), , flexible (not rigid), underconstrained (independent and not rigid).

% After that, define DR plans etc.

\begin{definition}
   In the context of this paper, a \textbf{graph} $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$.
\end{definition}

\begin{definition}
    The \textbf{density} of graph $G$ is
    \begin{equation}
        d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}
    \end{equation}
\end{definition}

\begin{definition}
    A graph is \textbf{independent} (or \textbf{sparse}) if \todo{define}.
\end{definition}

\begin{definition}
    A graph is \textbf{over-constrained} if, given constant $k$, there exists some induced subgraph $S\subseteq G$ such that $d(S) > k$.
\end{definition}

\begin{definition}
    A graph is \textbf{well-constrained} if, given constant $k$, $d(G) = k$ and for all induced subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).
\end{definition}

\begin{definition}
    A graph is \textbf{rigid} if, given constant $k$, there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.
\end{definition}

\begin{definition}
    A graph is \textbf{under-constrained} if, given constant $k$, $G$ is not rigid.
\end{definition}

\begin{definition}
    A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an over-constrained graph and (2) all of its subgraphs are also trivial.
    \todo{Maybe leave the following out until it's needed later?}
    In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.
\end{definition}

\begin{definition}
    The \textbf{decomposition-recombination (DR-) plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
    \begin{enumerate}
        \item The root of the tree `contains' $G$.
        \item For all nodes, $C$, that `contain' nontrivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item A node with a trivial subgraph is a leaf.
    \end{enumerate}

    % It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its well-constrained vertex-maximal proper subgraphs whose union is $G$ itself.

@@

    Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.
\end{definition}

\begin{definition}
    The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.
\end{definition}

\begin{definition}
    The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
\end{definition}

@@

$G$ is taken to be a graph with values $(V,E,w_V,w_E)$. The most important limitation of this paper is that we take $G$ to be well-constrained.
\todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.
